Crunching Large Graphs with Commodity Processors

### 2011-04-19 doc/hotpar2011/softxmt-hotpar2011.tex
minor eval change

The results of the experiment with six cores are shown in
Figure~\ref{fig:network-delay}. The runtime can still reach a
maximum rate of \mrps{173}\footnote{The throughput keeps increasing up to around 564 total concurrent references offered (at which point QPI is saturated), far more than the 36 we know the chip to support. This is because we have modeled the network latency by forcing coroutines to wait the extra time before using the data, so the physical miss buffers on our machine are not tied up any longer than usual.}, saturating the QPI link.  Little's law predicts that 300 concurrent references are required to achieve the estimated network rate of \mrps{100} when there is $3\mu s$ latency. We observe this: \mrps{100} is reached with about 53 coroutines per core. Although there may be other overheads in a full runtime, this experiment suggests there is potential to tolerate multi-node system latencies.

>>>>

The results of the experiment with six cores are shown in
Figure~\ref{fig:network-delay}. The runtime can still reach a
maximum rate of \mrps{173}\footnote{The throughput keeps increasing up to around 564 total concurrent references offered (at which point QPI is saturated), far more than the 36 we know the chip to support. This is because we have modeled the network latency by forcing coroutines to wait the extra time before using the data, so the physical miss buffers on our machine are not tied up any longer than usual.}, saturating the QPI link.  Little's law predicts that 300 concurrent references are required to achieve the estimated network rate of \mrps{100} when there is $3\mu s$ latency. The results agree: \mrps{100} is reached with about 53 coroutines per core. Although there will be other overheads in a full runtime, this experiment suggests there is potential to tolerate multi-node system latencies.
